Heuristics for the Score-Constrained Strip-Packing Problem

### 2018-05-09 PAPER/main.tex
algorithm pseudocode for mffd+

A prominent application of the COP is in a strip-packing problem brought to light as an open-combinatorial problem by \cite{goulimis2004}. Here, a set $\mathcal{I}$ of rectangular items of equal height $H$ made from cardboard are to be packed onto a strip of height $H$ from left to right. Each item $i \in \mathcal{I}$ has width $w_i \in \mathbb{Z}^{+}$, and possesses two vertical score lines, marked in predetermined places. A pair of knives mounted onto a bar cuts along the score lines of two adjacent items simultaneously, which allows the items to be folded with ease (see Figure \ref{fig:itemsknife}). However, by design, the scoring knives cannot be placed too close to one another, and as such have a ``minimum scoring distance'' (around 70mm in industry). The distances between each score line and the nearest edge on an item $i \in \mathcal{I}$ are the score widths, $a_i, b_i \in \mathbb{Z}^{+}$, assigned such that $a_i \leq b_i$. Since these score widths are not necessarily equal, an item $i$ can be positioned in one of two orientations: ``regular'', denoted $(a_i, b_i)$, or ``rotated'', denoted $(b_i, a_i)$, where the smaller of the two score widths $a_i$ is on the left- and right- hand side of the item respectively. Clearly, for two items to be placed alongside one another feasibly, the sum of the adjacent score widths must equal or exceed the minimum scoring distance, else the knives will not be able to score the items in the correct locations. Thus, the problem consists of finding a suitable ordering and orientation of the items such that the sum of every pair of adjacent score widths is greater than or equal to the minimum scoring distance. The left-hand score width of the first item and the right-hand score width of the last item on the strip are not adjacent to any other item, and are therefore ignored.

\begin{figure}[h!]	
	\centering
	\includestandalone[width=0.8\textwidth]{figures/itemsknife}
	\caption{Dimensions of an item $i \in \mathcal{I}$ in a regular orientation $(a_i, b_i)$, and a feasible alignment of two items that can be scored simultaneously.}	
	\label{fig:itemsknife}
\end{figure}

It can be seen that this problem is in fact equal to the COP, where each unordered pair in an instance $\mathcal{M}$ contains values corresponding to the score widths of an item, and $\tau$ is the minimum scoring distance.

@@

\begin{definition}
	\label{defn:scspp}
	Let $\mathcal{S} = \{S_1, S_2, ..., S_k\}$ be a set of strips of height $H$ and width $W$, and let $\mathcal{I}$ be a set of rectangular items of height $H$ and varying widths $w_i \in \mathbb{Z}^+ \leq W$ and score widths $a_i, b_i \in \mathbb{Z}^+$ such that $a_i \leq b_i$ and $a_i + b_i < w_i$ for each item $i \in \mathcal{I}$. Given a minimum scoring distance $\tau \in \mathbb{Z}^+$, the Score-Constrained Strip-Packing Problem (SCSPP) consists of finding the minimum number of strips $k$ required to pack all items in $\mathcal{I}$ such that the sum of every pair of adjacent score widths is greater than or equal to $\tau$.
\end{definition}

@@

\section{Solving the COP}
\label{sec:ahca}
We shall now present an exact polynomial-time algorithm for the COP. The underlying algorithm was originally created by \cite{becker2010}, and is used to determine whether or not a solution exists for a given instance. In our case, we have extended this algorithm so that, if a solution does indeed exist, the algorithm is able to formulate and present us with this final solution. This is especially useful for problems such as the previously mentioned strip-packing problem, where a solution is required in order to place the items in the correct order and orientation.
% We shall now present an algorithm for solving the COP, which operates by expressing the problem instance graphically.

@@

As we have seen, the values in $\mathcal{M}$ are arranged in pairs. This is represented in $G$ by adding a set of ``blue'' edges, $B$, that contains edges between vertices that are ``partners'', i.e. whose values make up a pair in $\mathcal{M}$, as shown in Figure \ref{fig:partners}. It can be seen that $B$ is a perfect matching in $G$, with $|B|= n+1$. Let the bijective function $p: V \to V$ associate each vertex with its partner, $p(v_i) = v_j$. Hence $B = \{(v_i, p(v_i)) : v_i \in V\}$.

Next, a set of ``red'' edges $R$ is added to $G$ that consists of edges between vertices whose sum equal or exceed $\tau$, provided they are not partners. This corresponds to the vicinal sum constraint in Defintion \ref{defn:cop}. Thus, we have an undirected graph $G$ with vertex set $V = \{v_1, ..., v_{2n+2}\}$ and two distinct edge sets $B$ and $R$ such that $B \cap R = \emptyset$. Figure \ref{fig:partners/threshold} illustrates and example construction of $G$.
% Equation $v_i + v_j \geq \tau$ provided $p(v_i) \neq v_j$, i.e. not partners
% Values are assigned from $\mathcal{M}$ in non-decreasing order, i.e. value assoc with v_1 \leq value assoc with v_2 etc..

@@

To find a matching $R' \subseteq R$, the following \textsc{Maximum Cardinality Matching} (MCM) algorithm can be executed, as suggested by \cite{mahadev1994} and \cite{becker2010}. Take each vertex $v_1, v_2,..., v_{2n+2}$ in turn, and select the edge in $R$ connecting $v_i$ to the highest indexed vertex $v_j$ that is not already incident to an edge in $R'$. Now add this edge $(v_i, v_j)$ to $R'$, and proceed to the next vertex until all the vertices have been assessed. The two vertices incident to each matching edge in $R'$ are now referred to as being ``matched''. Similarly to partners, let $m : V \to V$ be a bijective function that assigns each vertex with its match, $m(v_i) = v_j$. Then, $R' =\{(v_i, m(v_i)) : v_i \in V\}$.

@@

Clearly, if $|R'| < n+1$ after MCM are completed, there are insufficient red edges to form an alternating Hamiltonian cycle, and hence no feasible solution exists for the given instance $\mathcal{M}$ of the COP. Otherwise, $R'$ is a perfect matching of cardinality $n+1$ and $G'=(V, B \cup R')$ is a 2-regular graph, where each vertex is adjacent to its partner via an edge in $B$, and its match via an edge in $R'$ (see Figure \ref{fig:matching/mps}). $G'$ therefore consists of a collection of cyclic components $C_1, C_2, ..., C_q$. In the case where $G'$ comprises one component, i.e. $q = 1$, then this alternating cycle is in fact Hamiltonian, and therefore specifies a solution to the COP. However, if $q > 1$, the components of $G'$ must be combined to form a single alternating Hamiltonian cycle. To do this, a \textsc{Bridge Recognition} (BR) algorithm can be executed that selects suitable edges from $R$ that will replace certain edges in $R'$ in order to function as bridges and connect the components of $G'$.

BR operates by first ordering the edges in $R'$ such that the lower-indexed vertices of each edge are in increasing order and the higher-indexed vertices are in decreasing order, i.e. $(v_1, v_{2n+2}), (v_2, v_{2n+1}), ..., (v_{n+1}, v_{n+2})$. Any edges that cannot be placed in such an order are then removed from this list. For instance, in the example illustrated in Figure \ref{fig:matching/mps}, the edges would be sorted as follows: $(v_1, v_{14}), (v_2, v_{13}),(v_3, v_{12}),(v_4, v_{11}),(v_6, v_{10}),(v_7, v_8).$

Starting from the first edge in the list, BR then searches through the list to find an edge that meets the following conditions: 
\begin{enumerate*}[label={(\alph*)}]
	\item The lower-indexed vertex of the current edge and the higher-indexed vertex of the next edge in the list are adjacent via an edge in $R$; and
	\item The current edge and the next edge are members of different components on $G'$.
\end{enumerate*}
If these conditions are met, BR adds the current edge to a set $R_i$, and continues to add all succeeding edges in the list to $R_i$ provided that, for each edge, both conditions hold and the succeeding edge is not a member of a component of $G'$ that has an edge in $R_i$. Once there are no more valid edges available to add to $R_i$, BR resumes its search through the remaining edges in the list to find a new edge that meets the conditions, and can begin a new set $R_{i+1}$. The procedure terminates once the penultimate edge in the list has been assessed.

Now, one of the following three conditions holds.
\begin{enumerate}
\item In the event that BR has been unable to produce a single setthere are no suitable edges that can combine the components $C_1, C_2, ..., C_q$ of $G'$, and therefore an alternating Hamiltonian cycle for $G$ cannot be created. Thus, no feasible solution exists for the corresponding COP.

\item On the other hand, if there exists a set $R_i$ such that $|R_i| = q$, then the components of $G'$ can be merged together to form a single alternating Hamiltonian cycle. This is achieved by adding the red edge connecting the lower-indexed vertex of each edge in $R_i$ to the higher-indexed vertex of the next edge to $R'$ (for the final edge in $R_i$, add the red edge connecting its lower-indexed vertex to the higher-indexed vertex of the first edge). Any edges that appear in both $R_i$ and $R'$ are then removed from $R'$, so that $R'$ remains a perfect matching, and $R_i \cap R' = \emptyset$. $G'$ then consists of a single alternating Hamiltonian cycle, and hence a solution has been found.

\item Otherwise, it may be that multiple sets are required to connect the components of $G'$. For two sets $R_i$ and $R_j$ to ``overlap'', each set must have one edge from the same component in $G'$, with the other edges in each set being from different components. For example, if $R_1$ has two edges, one from component $C_1$ and one from component $C_2$, and $R_2$ has three edges that are members of $C_2$, $C_3$ and $C_4$, then $R_1$ and $R_2$ are said to overlap, since they each possess an edge $C_2$, but the other edges in the sets are from different components. Hence, a selection of sets from $R_1, R_2, ..., R_k$ need to be found such that each set overlaps with at least one other set, and each component has at least one edge in one of the selected sets. If such a collection of sets exists, then the components of $G$ can be merged to create an alternating Hamiltonian cycle by applying the connecting procedure above to every set in the collection.
% Refer to figures
\end{enumerate}
Using the instance illustrated in the figures as an example, the edges $(v_3, v_{12})$ and $(v_4, v_{11})$ are in the set $R_1$ formed by $BR$, as they are members of different components ($(v_3, v_{12}) \in C_1$ and $(v_4, v_{11}) \in C_2$ as seen in Figure \ref{fig:mps}), and $(v_3, v_{11}) \in R$. Note that since $v_4$ and $v_{11}$ are adjacent, $v_4$ must also be adjacent to $v_{12}$, i.e. $(v_4, v_{12}) \in R$, since the value associated with $v_12$ is greater than or equal to the value associated with $v_{11}$. Then, as $|R_1| = q$, the edges $(v_3, v_{12})$ and $(v_4, v_{11})$ are removed from $R'$ and replaced by the edges $(v_3, v_{11})$ and $(v_4, v_{12})$ from $R$, as shown in Figure \ref{fig:connect/cycle}. Removing the dominating vertices and any incident edges results in an alternating Hamiltonian path, which corresponds to a feasible solution $\mathcal{T}$.

@@

@@

\textbf{Speed $n$ = 1000}
\begin{itemize}
	\item MFFD $W = 5000$ Average speed = 159.68755ms/instance
	\item MFFD $W = 2500$ Average speed = 157.92673ms/instance
	\item MFFD $W = 1250$ Average speed = 154.45345ms/instance
	\item PS $W = 5000$ Average speed = 168.77291ms/instance
	\item PS $W = 2500$ Average speed = 176.81209ms/instance
	\item PS $W = 1250$ Average speed = 201.522ms/instance
	\item MFFD$^+$ $W = 5000$ Average speed = 825.59964ms/instance
	\item MFFD$^+$ $W = 2500$ Average speed = 
	\item MFFD$^+$ $W = 1250$ Average speed = 
\end{itemize}

>>>>

A prominent application of the COP is in a strip-packing problem brought to light as an open-combinatorial problem by \cite{goulimis2004}. Here, a set $\mathcal{I}$ of rectangular items of equal height $H$ made from cardboard are to be packed onto a strip of height $H$ from left to right. Each item $i \in \mathcal{I}$ has width $w_i \in \mathbb{Z}^{+}$, and possesses two vertical score lines, marked in predetermined places. A pair of knives mounted onto a bar cuts along the score lines of two adjacent items simultaneously, which allows the items to be folded with ease (see Figure \ref{fig:itemsknife}). However, by design, the scoring knives cannot be placed too close to one another, and as such have a ``minimum scoring distance'' (around 70mm in industry). The distances between each score line and the nearest edge on an item $i \in \mathcal{I}$ are the score widths, $a_i, b_i \in \mathbb{Z}^{+}$ where $a_i + b_i < w_i$, assigned such that $a_i \leq b_i$. Since these score widths are not necessarily equal, an item $i$ can be positioned in one of two orientations: ``regular'', denoted $(a_i, b_i)$, or ``rotated'', denoted $(b_i, a_i)$, where the smaller of the two score widths $a_i$ is on the left- and right- hand side of the item respectively.

\begin{figure}[H]	
	\centering
	\includestandalone[width=0.8\textwidth]{figures/itemsknife}
	\caption{Dimensions of an item $i \in \mathcal{I}$ in a regular orientation $(a_i, b_i)$, and a feasible alignment of two items that can be scored simultaneously.}	
	\label{fig:itemsknife}
\end{figure}

Clearly, for two items to be placed alongside one another feasibly, the sum of the adjacent score widths must equal or exceed the minimum scoring distance, else the knives will not be able to score the items in the correct locations. Thus, the problem consists of finding a suitable ordering and orientation of the items such that the sum of every pair of adjacent score widths is greater than or equal to the minimum scoring distance. The left-hand score width of the first item and the right-hand score width of the last item on the strip are not adjacent to any other item, and are therefore ignored.

It can be seen that this problem is in fact equal to the COP, where each unordered pair in an instance $\mathcal{M}$ contains values corresponding to the score widths of an item, and $\tau$ is the minimum scoring distance. Figure \ref{fig:items/aligned} shows the example instance $\mathcal{M}$ of the COP from above as a packing problem.
% vsc = sum of every adj pair of score widths \geq \tau.

\begin{figure}	
	\centering
	\begin{subfigure}[h]{0.44\textwidth}
		\includestandalone[width=\textwidth]{figures/items}
		\label{fig:items}\vspace{10pt}
	\end{subfigure} 
	\begin{subfigure}[h]{0.7\textwidth}
		\includestandalone[width=\textwidth]{figures/itemsaligned}
		\label{fig:itemsaligned}
	\end{subfigure}
	\caption{Example of the strip-packing problem, where the sum of each pair of adjacent score widths must be greater than or equal to $\tau = 7$. From instance $\mathcal{M}$ above.}
	\label{fig:items/aligned}
\end{figure}

@@

\begin{definition}
	Let $\mathcal{I}$ be a set of rectangular items of height $H$ with varying widths $w_i \in \mathbb{Z}^+$ and score widths $a_i, b_i \in \mathbb{Z}^+$ for each item $i \in \mathcal{I}$. Given a minimum scoring distance $\tau \in \mathbb{Z}^+$, the Score-Constrained Strip-Packing Problem (SCSPP) consist of finding the minimum number of strips of height $H$ and width $W$ required to pack all items in $\mathcal{I}$ such that the sum of every pair of adjacent score widths is greater than or equal to $\tau$. %and that no strip is overfilled.
\end{definition}

@@

\section{Solving the COP}
\label{sec:ahca}
We shall now present an exact polynomial-time algorithm for the COP. The underlying algorithm was originally created by \cite{becker2010}, and is used to determine whether or not a solution exists for a given instance. In our case, we have extended this algorithm so that, if a solution does indeed exist, the algorithm is able to formulate and present us with this final solution. This is especially useful for problems such as the previously mentioned strip-packing problem, where a solution is required in order to place the items in the correct order and orientation.

@@

As we have seen, the values in $\mathcal{M}$ are arranged in pairs. This is represented in $G$ by adding a set of ``blue'' edges, $B$, that contains edges between vertices that are ``partners'', i.e. whose values make up a pair in $\mathcal{M}$, as shown in Figure \ref{fig:partners}. By introducing a bijective function $p: V \to V$ that associates each vertex with its partner, $p(v_i) = v_j$, we can denote this set of edges as $B = \{(v_i, p(v_i)) : v_i \in V\}$. It can be seen that $B$ is a perfect matching in $G$, with $|B| = n+1$.

Next, a set of ``red'' edges $R$ is added to $G$ that consists of edges between vertices whose sum equal or exceed $\tau$, provided they are not partners. This corresponds to the vicinal sum constraint in Defintion \ref{defn:cop}. Thus, we have an undirected graph $G$ with vertex set $V = \{v_1, ..., v_{2n+2}\}$ and two distinct edge sets $B$ and $R$ such that $B \cap R = \emptyset$. Figure \ref{fig:partners/threshold} illustrates and example construction of $G$.
% Equation $v_i + v_j \geq \tau$ provided $p(v_i) \neq v_j$, i.e. not partners
% Values are assigned from $\mathcal{M}$ in non-decreasing order, i.e. value assoc with v_1 \leq value assoc with v_2 etc..
% "This corresponds to the vsc in Defn 1" - values that can be aligned alongside one another that are not part of the same unordered pair in M, hence why they cannot be partners on the graph G, must be from different unordered pairs.

@@

To find a matching $R' \subseteq R$, the following \textsc{Maximum Cardinality Matching} (MCM) algorithm can be executed, as suggested by \cite{mahadev1994} and \cite{becker2010}. Take each vertex $v_1, v_2,..., v_{2n+2}$ in turn, and select the edge in $R$ connecting $v_i$ to the highest-indexed vertex $v_j$ that is not already incident to an edge in $R'$. Now add this edge $(v_i, v_j)$ to $R'$, and proceed to the next vertex until all the vertices have been assessed. The two vertices incident to each matching edge in $R'$ are now referred to as being ``matched''. Similarly to partners, let $m : V \to V$ be a bijective function that assigns each vertex with its match, $m(v_i) = v_j$. Then, we can denote this matchin set as $R' =\{(v_i, m(v_i)) : v_i \in V\}$.

@@

Clearly, if $|R'| < n+1$ after MCM has completed, there are insufficient red edges to form an alternating Hamiltonian cycle, and hence no feasible solution exists for the given instance $\mathcal{M}$ of the COP. Otherwise, $R'$ is a perfect matching of cardinality $n+1$ and the spanning subgraph $G'=(V, B \cup R')$ is a 2-regular graph, where each vertex $v_i \in V$ is adjacent to its partner $p(v_i)$ via a blue edge in $B$, and its match $m(v_i)$ via a red edge in $R'$ (see Figure \ref{fig:matching/mps}). $G'$ therefore consists of a collection of cyclic components $C_1, C_2, ..., C_q$. In the case where $G'$ comprises one component, i.e. $q = 1$, then this alternating cycle is in fact Hamiltonian, and therefore specifies a solution to the COP. However, if $q > 1$, the components of $G'$ must be combined to form a single alternating Hamiltonian cycle. To do this, a \textsc{Bridge Recognition} (BR) algorithm can be executed that selects suitable edges from $R$ that will replace certain edges in $R'$ in order to function as bridges and connect the components of $G'$.

BR operates by first ordering the edges in $R'$ such that the lower-indexed vertices of each edge are in increasing order and the higher-indexed vertices are in decreasing order, i.e. $(v_1, v_{2n+2}), (v_2, v_{2n+1}), ..., (v_{n+1}, v_{n+2})$. Any edges that cannot be placed in such an order are then removed from this list. For instance, in the example illustrated in Figure \ref{fig:matching/mps}, the edges would be sorted as follows: $(v_1, v_{14}), (v_2, v_{13}),(v_3, v_{12}),(v_4, v_{11}),(v_6, v_{10}),(v_7, v_8)$.
% (v5, v9) removed from list, not matched with highest-indexed vertex in MCM since it was v10 and v10 is v5's partner.

Starting from the first edge in the list, BR then searches through the list to find an edge that meets the following conditions: 
\begin{enumerate*}[label={(\alph*)}]
	\item The lower-indexed vertex of the current edge and the higher-indexed vertex of the next edge in the list are adjacent via an edge in $R$; and
	\item The current edge and the next edge are members of different components on $G'$.
\end{enumerate*}
If these conditions are met, BR adds the current edge to a set $R_i$, and continues to add all succeeding edges in the list to $R_i$ provided that, for each edge, both conditions hold and the succeeding edge is not a member of a component of $G'$ that has an edge in $R_i$. Once there are no more valid edges available to add to $R_i$, BR resumes its search through the remaining edges in the list to find a new edge that meets the conditions, and can begin a new set $R_{i+1}$. The procedure terminates once the penultimate edge in the list has been assessed.
% (a) (v_i,m(v_{i+1})) \in R
% (b) (v_i, m(v_i)) \in C_k, (v_{i+1}, m(v_{i+1})) \in C_l, k \neq l

Now, one of the following three conditions holds.
\begin{enumerate}
\item In the event that BR has been unable to produce a single set, there are no suitable edges that can combine the components $C_1, C_2, ..., C_q$ of $G'$, and therefore an alternating Hamiltonian cycle for $G$ cannot be created. Thus, no feasible solution exists for the corresponding COP.

\item On the other hand, if there exists a set $R_i$ such that $|R_i| = q$, then the components of $G'$ can be merged together to form a single alternating Hamiltonian cycle. This is achieved by adding the red edge connecting the lower-indexed vertex of each edge in $R_i$ to the higher-indexed vertex of the next edge to $R'$ (for the final edge in $R_i$, add the red edge connecting its lower-indexed vertex to the higher-indexed vertex of the first edge). Any edges that appear in both $R_i$ and $R'$ are then removed from $R'$, so that $R'$ remains a perfect matching and $R_i \cap R' = \emptyset$. $G'$ then consists of a single alternating Hamiltonian cycle, and hence a solution has been found.
% add edges (v_i, m(v_{i+1})) for i \in {1, 2, ..., |R_i| -1} from R to R', and then the edge (v_{|R_i|}, m(v_1)) from R to R'

\item Otherwise, it may be that multiple sets are required to connect the components of $G'$. For two sets $R_i$ and $R_j$ to ``overlap'', each set must have one edge from the same component in $G'$, with the other edges in each set being from different components. For example, if $R_1$ has two edges, one from component $C_1$ and one from component $C_2$, and $R_2$ has three edges that are members of $C_2$, $C_3$ and $C_4$, then $R_1$ and $R_2$ are said to overlap, since they each possess an edge $C_2$, but the other edges in the sets are from different components. Hence, a selection of sets need to be found such that each set overlaps with at least one other set, and each component has at least one edge in one of the selected sets. If such a collection of sets exists, then the components of $G$ can be merged to create an alternating Hamiltonian cycle by applying the connecting procedure above to every set in the collection.
% Refer to figures
\end{enumerate}
Using the instance illustrated in the figures as an example, the edges $(v_3, v_{12})$ and $(v_4, v_{11})$ are in the set $R_1$ formed by BR, as they are members of different components ($(v_3, v_{12}) \in C_1$ and $(v_4, v_{11}) \in C_2$ as seen in Figure \ref{fig:mps}), and $(v_3, v_{11}) \in R$. Note that since $v_4$ and $v_{11}$ are adjacent, $v_4$ must also be adjacent to $v_{12}$, i.e. $(v_4, v_{12}) \in R$, since the value associated with $v_{12}$ is greater than or equal to the value associated with $v_{11}$. Then, as $|R_1| = q$, the edges $(v_3, v_{12})$ and $(v_4, v_{11})$ are removed from $R'$ and replaced by the edges $(v_3, v_{11})$ and $(v_4, v_{12})$ from $R$, as shown in Figure \ref{fig:connect/cycle}. Removing the dominating vertices and any incident edges results in an alternating Hamiltonian path, which corresponds to a feasible solution $\mathcal{T}$.

@@

\begin{algorithm}[H]
	\caption{MFFD$^+$}
	\label{alg:mffd+}
	\begin{algorithmic}[1]
		\State Sort items in $\mathcal{I}$ in order of non-increasing widths $w_i$.
		\For{$i \gets 1 \To |\mathcal{I}|$}
			\State $j \gets 1$, packed $\gets \False$
			\While{not packed}
				\If{$S_j \in \mathcal{S}$ and $\sum_{i=1}^{|S_j|}w_i + w_i \leq W$}
					\State Run AHC
					\If{AHC returns feasible solution}
						\State $S_j \gets S_j \cup i$ in order of feasible solution
						\State packed $\gets \True$
					\Else \hspace{0.2mm} $j \gets j + 1$					 
					\EndIf
				\ElsIf{$S_j \notin \mathcal{S}$}
					\State $S_j \gets S_j \cup i$ in regular orientation
					\State $\mathcal{S} \gets \mathcal{S} \cup S_j$	
					\State packed $\gets \True$
				\EndIf
			\EndWhile	
		\EndFor
		\Return $\mathcal{S}$
	\end{algorithmic}	
\end{algorithm}

@@

\textbf{Speed $n$ = 1000}
\begin{itemize}
	\item MFFD $W = 5000$ Average speed = 159.68755ms/instance
	\item MFFD $W = 2500$ Average speed = 157.92673ms/instance
	\item MFFD $W = 1250$ Average speed = 154.45345ms/instance
	\item PS $W = 5000$ Average speed = 168.77291ms/instance
	\item PS $W = 2500$ Average speed = 176.81209ms/instance
	\item PS $W = 1250$ Average speed = 201.522ms/instance
	\item MFFD$^+$ $W = 5000$ Average speed = 825.59964ms/instance
	\item MFFD$^+$ $W = 2500$ Average speed = 744.73509ms/instance
	\item MFFD$^+$ $W = 1250$ Average speed = 434.67655ms/instance
\end{itemize}
